Empty Homes V1

### 2017-07-06 LowUseEngland.Rmd
All kinds of debug

@@

>>>>

housing studies
internat jouranl housing policy

becky tunstall housing space inequality

niall may - between 1990 - 1995 hoomes built loads of homes built small number owned

positive money

@@

#business rates
```{r}
setwd(file.path(basewd, "Business rates"))
SlakelBuss <- read_csv("sldc-business-rates-full-list-07042017.csv")

test <- SlakelBuss %>% group_by(PropertyDescription) %>% 
  summarise(counts = n())

test2 <- test %>% filter(grepl("SELF", PropertyDescription))

test2$counts %>% sum

SlakelBuss<-SlakelBuss %>% 
  rename(Postcode = PropPostCode) %>%
  mutate(Postcode = gsub(" ", "" , Postcode)) %>%
  filter(grepl("SELF", PropertyDescription)) %>% left_join(., PstCdLSOA.raw, by = "Postcode") %>%
    mutate(LSOA_CODE = lsoa11cd,
         `Exemption type` = "Discount Class B (Furnished & Unocc)") %>%
  select(LSOA_CODE, `Exemption type`)

    test <- SlakelBuss %>% group_by(LSOA_CODE) %>%
    summarise(HomesB = n())

#several hundred un-matchable postcodes
test2 <- SlakelBuss%>% 
  mutate(testme = is.na(lsoa11cd)) %>%
  group_by(AccountName, testme) %>% 
  summarise(count = n()) %>%
  rename

setwd(file.path(RegionsComp, "Region North West"))
SLakelandCUMBRIADATA2 <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)[,1:4] %>%
  bind_rows(SlakelBuss) %>%
    StructureData(., lowuse=2:9)

SLakelandCUMBRIADATA3 <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)[,1:4] %>%
    StructureData2(., lowuse=2:9, Business = SlakelBuss)

MakeLeaflet(SLakelandCUMBRIADATA2)

MakeLeaflet(SLakelandCUMBRIADATA3)

plot(SLakelandCUMBRIADATA$LowUsePerc,SLakelandCUMBRIADATA3$LowUsePerc)

test <- data.frame(Biz =SLakelandCUMBRIADATA3$LowUsePerc, Norm = SLakelandCUMBRIADATA$LowUsePerc ) %>%
  mutate(diff = Biz-Norm)

test %>% ggplot(aes(x= diff)) + geom_density()

### 2017-07-06 LowUseLondon.Rmd
Final Pre Blog
Last update before publsihing the 3rd blog
All kinds of debug

#All London With missing Boroughs
PlotMap(Lambethinfo, AG)

@@

#Hammersmith 
Hammersmithinfo <- read_excel("Hammersmith.xls", skip = 1 ) %>% filter(!is.na(Ward) ) %>% 
  bind_cols(., filter(wardnames,LAD11NM == "Hammersmith and Fulham")) %>% select(-Ward) %>%
  mutate(LowUse = `Second (B)` + `Empty Unocc`+ LTE + Premium, Empty = LowUse - `Second (B)`) %>%
  SemiDataStructure

@@

#Hull
```{r}

>>>>

#All London With missing Boroughs
PlotMap(Hammersmithinfo, AG)

 test <- list("Hammersmithinfo", "Chelseainfo") %>% map_df(~eval(parse(text=.x)))

 Hammersmithinfo %>% filter(LSOA_CODE!="E01001866") %>% 
   bind_rows(Chelseainfo) %>%
   MakeLeaflet(.)

 PlotMap(test, AG)
test %>% MakeLeaflet(.)

test2 <- filter(test, LSOA_CODE=="E01001866")

@@

# #Hammersmith 
# Hammersmithinfo <- read_excel("Hammersmith.xls", skip = 1 ) %>% filter(!is.na(Ward) ) %>% 
#   bind_cols(., filter(wardnames,LAD11NM == "Hammersmith and Fulham")) %>% select(-Ward) %>%
#   mutate(LowUse = `Second (B)` + `Empty Unocc`+ LTE + Premium, Empty = LowUse - `Second (B)`) %>%
#   SemiDataStructure

@@

```{r}
